Stack Safety as a Security Property

### 2020-07-09 main.tex
More on observable properties

\paragraph*{Eager vs Lazy Stack Safety}

@@

\leo{Not sure how much of the following could go after the lazy stack safety property}
These \emph{lazy policies} admit more efficient implementations while being
harder to test, given that potential violations may or may not materialize,
requiring in turn additional bookkeeping. However, a critical observation is
that the depth-based tagging scheme discussed so far with fail when combined
with a lazy policy. The reason for this is that because tags are not set and
cleared on function entry and exit points, stale tags may persist after a given
call, and a subsequent call sharing the same depth as the old call may access
memory contents tagged with the stale tags of a previous activation.
\rb{Again, example?}

The lazy policy can be repaired if, instead of tagging each function activation
with its depth in the stack, we generate a fresh activation identifier on each
call, which allows the policy to identify stale tags from previous activations.
Under this stricted tagging discipline, the eager policy behaves almost exactly
like its lazy counterpart. A related mechanism was explored in the Static
Authorities policy of \citet{DBLP:conf/sp/RoesslerD18}, which associates a
unique activation identifier to each function, which is however shared by all
activations of the same function in order to obtain good cacheability of tag
rules.

\rb{Parts of this discussion feel somewhat out of order...}

@@

  A lazy policy permits some violations of integrity or confidentiality,
  justified because a truly harmful violation will be caught later.
  In a typical lazy version of the tag policy, writes are always permitted,
  but tagged to identify the context in which they were written. But reads
  check that the value read was written by the current context and fail-stop
  if it wasn't. So, if a callee makes an illegal write to its caller, when the
  caller tries to read it the policy will catch the error.

  The natural question is, how do we characterize the protections provided
  by these policies once stack safety is broken? How does a harmful violation
  that must be caught later differ from a harmless one? The properties in this
  section use the observation model to draw this distinction.

    \sna{Use the \(n\)-transition language above in all of these.}

\apt{Need some intro text here.}

@@

\apt{Words needed to connect these ideas back to the lazy policies which motivated them in the first place!}

>>>>

\paragraph*{Eager vs Lazy Policies}

@@

These \emph{lazy policies} admit more efficient implementations, but they
deliberately allow violations of stack integrity. So it becomes important to
characterize what alternative property these policies ought to implement.

\sna{moved a lot of discussion to after property, along with Rob's
     comments on it}

@@

  A lazy policy permits some violations of integrity or confidentiality,
  justified because a truly harmful violation will be caught later.
  The natural question is, how do we characterize the protections provided
  by these policies once stack safety is broken? How does a harmful violation
  that must be caught later differ from a harmless one? The properties in this
  section use the observation model to draw this distinction.

@@

    \paragraph{Connection to Policies}

    Observable properties allow us defer enforcement until a property
    violation would become visible, as in lazy policies. But by formalizing
    the connection to the eager policy, we can identify when lazy policies
    miss violations that can become visible. The basic lazy tag policy from
    \citet{DBLP:conf/sp/RoesslerD18} tags written memory with the depth in the
    stack at which it was written, and enforces that it must be read from the
    same depth. This allows violations of observable stack safety!
    Say we have functions {\tt foo}, {\tt bar} and {\tt baz}, where {\tt foo}
    calls {\tt bar}, and then after {\tt bar} returns {\tt foo} calls
    {\tt baz}. Since {\tt bar} and {\tt baz} are at the same stack depth, if
    {\tt bar} writes to {\tt foo}'s frame, {\tt baz} can then read the tainted
    write and use it to create an observable difference that violates both
    observable integrity and confidentiality without violating the policy.
    This can be fixed by generating distinct tags per-activation.

    The lazy policy can be repaired if, instead of tagging each function 
    activation with its depth in the stack, we generate a fresh activation
    identifier on each call, which prevents a program from exploiting stale
    tags from previous activations. A related mechanism was explored in the
    Static Authorities policy of \citet{DBLP:conf/sp/RoesslerD18}, which
    associates a unique activation identifier to each function, which is
    however shared by all activations of the same function in order to obtain
    good cacheability of tag rules. Static Authorities comes closer to
    observable stack safety, though the example above would still exist
    if {\tt bar} and {\tt baz} were merged into a single function that tracked
    whether it had been called previously and changed its behavior accordingly.

  \paragraph{Relation to Stack Safety}
